---
title: "DATA607_Week3_Assignment"
author: "Matt Mecoli"
date: "2/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Environment

Loading packages and setting up environment. 

```{r environment, eval=TRUE}
library(tidyverse)
library(htmlwidgets)
```

### Data Import 

Importing data into a data frame.

```{r data_import, eval=TRUE}
college_majors = read.csv("data/majors-list.csv") 
```

### Assignment Questions 

Work product necessary to answer questions. 

#### Question 1

```{r find_majors, eval=TRUE}
MajorVec <- as.vector(college_majors$Major)
str_detect(MajorVec, "DATA|STATISTICS")
```


#### Question 2

```{r question_2, eval=TRUE}
vector_output <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange" [5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  [9] "elderberry"   "lime"         "lychee"       "mulberry"    [13] "olive"        "salal berry"'

test_str <- str_replace_all(vector_output, "[:cntrl:]|[:digit:]|\\[|\\]",' ')
test_str2 <- str_replace_all(test_str, " \\\"", ' ')
test_str3 <- str_replace_all(test_str2, "\\s+", ' ')
test_str4 <- str_replace_all(test_str3, "\"\\s", '_')
test_str5 <- str_replace_all(test_str4, "\"", '')
test_str6 <- str_trim(test_str5)
back_to_vector <- c(str_split(test_str6, '_'))[[1]]
back_to_vector
```

#### Question 3

I'm assuming here that we're omitting escape characters because otherwise these would not match anything because it's missing the escape character.
 
1) (.)\1\1 Will match to the character appearing three times in a row. Ex. 111

2) “(.)(.)\2\1” Will match to a palindrome of type 1,2,2,1.

3) (..)\1 Will match any group of two characters repeated once. Ex. 1212

4) “(.).\1.\1” Backreferences refer to the indicated referenc characters. So a character, followed by any character, follow by the first character, followed by any character, followed by the first character. Ex. 12131.  

5) "(.)(.)(.).*\3\2\1" Three of any chracters follow by any number of other characters and then the first three characters in reverse positional order. So like 123banana321. 

#### Question 4

1) “^(.)(.*\\1$) "

The chracter we want in the first position followed by any number of characters and then the character in the last position. 

2) “([A-Za-z][A-Za-z]).*\\1”

So any alpha character followed by any alpha character, followed by any number of other characters, followed by the original two alpha characters repeated once. 

3) “([A-Za-z]).*\\1.*\\1"

Any alpha chracter followed by any other characters, followed by the first, follow by any number, followed by the first. 

